\documentclass[]{deedy-resume-openfont}

% Date command
\usepackage[absolute]{textpos}
\usepackage[UKenglish]{isodate}
\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}
\newcommand{\lastupdatedon}{\begin{textblock}{60}(155,0)
\color{date}\fontspec[Path = fonts/raleway/]{Raleway-ExtraLight}\fontsize{8pt}{10pt}\selectfont 
Last Updated on \today
\end{textblock}}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdatedon

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Avinash}{Madhukar}{ \urlstyle{same}\url{https://chshbh.github.io} \\
\href{mailto:madhukar.avinash14@stu.upes.ac.in}{madhukar.avinash14@stu.upes.ac.in} | 875.558.6645
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Undergraduate}
\descript{UPES \\
B.tech in Computer Science}
\location{Expected May 2018 | Dehradun, India}
School of Computer Science \\
Semester (7)\\
\location{ Cum. GPA: 2.74 / 4.0 }
\sectionsep

\subsection{School}
\descript{Modern International School}
\location{Grad. May 2013|  Delhi, India}
Percentage: 72.4
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/chshbh}{\custombold{chshbh}} \\
Codechef:// \href{https://www.codechef.com/users/it4ch1_m8}{\custombold{chshbh}} \\
Hackerrank:// \href{https://www.hackerrank.com/chshbh}{\custombold{chshbh}} \\
Codeforces:// \href{http://codeforces.com/profile/chshbh}{\custombold{chshbh}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{MOOCs}
MITx 6.00.1x, edX \\
MITOpenCourseWare 6.006, Fall 2011\\
\sectionsep

\subsection{Undergraduate}
Mathematics for Computer Science \\
Data Structures \\
Design and Analysis of Algorithms \\
Operating System \\
Computer System Architecture \\
OOPS Programming \\
Theory of Computation \\
Introduction to Open Source \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Basic:}
\textbullet{} C/C++ \textbullet{} Java \textbullet{} Rust \\
\location{Intermediate:}
\textbullet{}Python2/3
\subsection{Tools and Packages}
\textbullet{} git \textbullet{} make \textbullet{} cProfile  
\subsection{Development Environment}
\textbullet{} Sublime Text 3 \textbullet{} nano \textbullet{} Code::Blocks \textbullet{} Netbeans
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intern}
\runsubsection{Identification of Terrestrial Global Biodiversity Hotspots}
\descript{| IIRS, ISRO}
\location{Predicting new biodiversity hotspots hypothetically using the data generated by remote sensing and GIS.}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Using multi-criteria-based analysis and spatial decision support system to get a better estimate of the spatial and temporal changes in hotspots in real time.
\item  By using WorldClim data and world topographical data with species distribution model to prepare a workable uniform approach in determining the hotspots.
\end{tightemize}
\sectionsep



\section{Project}

\runsubsection{YATE, Yet Another Text Editor}
\descript{| Aug 2016 - Nov 2016  }
\location{A lightweight “GUI-like” text editor using Python, that automatically generates ciphertext, message digest and Base64 text files.}
\begin{tightemize}
\item Created a primitive text editor using ncurses(Python) library.
\item Cryptographic Algorithms : AES128 Encryption, SHA256 Hashing and Base64 Encoding.

\end{tightemize}
\sectionsep

\runsubsection{ Password Manager}

\location{A personal password manager.}
\begin{tightemize}
\item SqlCipher Database is used to encrypt the database file with AES.
\item peewee ORM is used to map and interact with the database.
\item Create, store, edit and generate password, that allows user to use a single "master" password to
generate unique password for all the sites and services.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH/RESPONSIBILITY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Responsibility}
\runsubsection{Class Representative}
\descript{| Nov 2015 - Present}
\location{UPES, \\
Gather views from peers regarding various aspects of their course and to communicate
those to members of staff.}
\sectionsep

\runsubsection{Senior Member}
\descript{| Sept 2016 - Present}
\location{Programming Group, \\
Conducting classes and organizing discussion panel on Programming and Open Source.}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS/ACHIEVEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\begin{tabular}{rll}
2016     & 3413/58520 & Google Code Jam, Qualification Round\\
2016     & 2476/13388 & Codechef Snackdown, Qualification Round\\
2016     & 596/9077   & Codechef Snackdown, Elimination Round\\
2017	 & 1248/21048 & Codechef Snackdown, Qualification Round\\
2016     & 15\textsuperscript{th}  & Master the Mainframe, IBM\\
2017     & Cleared & Facebook HackerCup, Qualification Round\\
2016     & Participated & dgplug Summer Training\\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
